### 2025-09-25 paper/sec/evaluation.tex
Merge main.

To what extent can LLMs accurately interpret quantitative and semi-quantitative claims in scholarly text as
data queries? We examine performance across a range of linguistic idioms (e.g. averages, percentages, min/max,
ranks, as summarised in Table~\ref{tab:natural-language-forms}) and investigate how accuracy varies with task
complexity, measured (somewhat crudely) by the number of query sub-expressions (e.g. retrieval, aggregation,
or arithmetic) present in the gold solution.

>>>>

To what extent can LLMs accurately interpret quantitative and semi-quantitative claims in scholarly text as
data queries? We examine performance across a range of linguistic idioms (e.g. averages, percentages, min/max,
ranks, as summarised in Table~\ref{tab:natural-language-forms}) and investigate how accuracy varies with task
complexity, measured (somewhat crudely and approximately) by the number of query sub-expressions (e.g.
retrieval, aggregation, or arithmetic) present in the gold solution.
